SMT-Boosted Security Types for Low-Level MPC

### 2025-05-04 esop25/slides.tex
checkpoint

  Existing HLLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques mostly manual.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item Automated type analysis for security properties, with correctness based on
    \cemph{hyperproperties}\footnote{Skalka and Near, PPDP 2024}.
  \item Our type analysis leverages an \cemph{SMT finite fields theory}\footnote{Ozdemir et. al, CAV 2023} for:
    \begin{itemize}
    \item \cemph{Correctness}
    \item \cemph{Confidentiality}
    \item \cemph{Integrity}
    \end{itemize}
  \end{itemize}

@@

\begin{frame}{What's an MPC Protocol?}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations $(+,-,*)$ in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item Clients are distributed and communicate via \cemph{message passing}.
  \item Any client can be corrupted by the adversary, who can then see their messages.
  \item The \cemph{output} is made \emph{publicly available} by $\prog$.
  \end{itemize}
  \cemph{The output may leak secret information to an adversary} trying to
  guess secret values, since it depends on inputs.

@@

  \cemph{Confidentiality} means that protocol messages don't enable the adversary
  to make better guesses than the output alone.

@@

  Low-level, probabilistic protocols are defined in terms of basic variable types
  (identifiers $x$ distinguish them):
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\flip{x}$: uniformly random samples from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \end{itemize}
  \emph{Computations} are normal field operations on variables-- addition (+), multiplication (*),
  and additive inverse (-).

@@

  The cvc5 Finite Fields Theory supports automated satisfiability checking of equational
  constraint definitions $\eqs$ over prime fields $\mathcal{F}_{p}$.

@@

\begin{frame}[fragile]{Compositional Integrity Typing in Prelude}
  \small{
  \begin{verbatimtab}
MACOK(x, i1, i2)
  { m[x++"m"]@i2 ==
    m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2) }

>>>>

  Existing high-level PLs rely on low-level MPC protocols with correctness
  assumed.
  \begin{itemize}
  \item Distinct features, e.g., probabilistic sampling.
  \item Existing proof techniques mostly manual.
  \end{itemize}
  Our contributions:
  \begin{itemize}
  \item Language design for low-level protocol definitions.
  \item Automated type analysis for security properties, with correctness based on
    \cemph{hyperproperties}\footnote{Skalka and Near, PPDP 2024}.
  \item Our type analysis leverages an \cemph{SMT finite fields theory}\footnote{Ozdemir et. al, CAV 2023} for:
    \begin{itemize}
    \item \cemph{Correctness}
    \item \cemph{Confidentiality}
    \item \cemph{Integrity}
    \end{itemize}
  \end{itemize}

@@

\begin{frame}{What's an MPC Protocol?}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations $(+,-,*)$ in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item Clients are distributed and communicate via \cemph{message passing}.
  \item Any client can be corrupted by the adversary, who can then see their messages.
  \item The \cemph{output} $=\idealf$ is made \emph{publicly available} by $\prog$.
  \end{itemize}
  \cemph{$\idealf$ may expose some information to an adversary} trying to
  guess secret values, since it depends on inputs.

@@

  \cemph{Confidentiality} means that the protocol doesn't enable the adversary
  to make better guesses than $\idealf$.

@@

  In our language Overture, low-level, probabilistic protocols are defined in
  terms of basic variable types (identifiers $x$ distinguish them):
  \begin{itemize}
  \item $\secret{x}$: secret values in $\mathbb{F}_p$.
  \item $\mesg{x}$: messages received during the protocol.
  \item $\flip{x}$: uniformly random samples from $\mathbb{F}_p$ (implemented with
    a random tape semantics).
  \end{itemize}
  \emph{Computations} are normal field operations on variables-- addition (+), multiplication (*),
  and additive inverse (-).

@@

  The cvc5 Finite Fields Theory supports automated satisfiability checking of equational
  constraint definitions $\eqs$ over prime fields $\mathbb{F}_{p}$.

@@

\section{SMT Boosting: Integrity}
\begin{frame}[fragile]{Compositional Integrity Typing in Prelude}
  \small{
  \begin{verbatimtab}
MACOK(x, i1, i2)
  { m[x++"m"]@i2 ==
    m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2) }
